Supplement for: Carbon cycling in mature and regrowth forests globally: a macroecological synthesis based on the global Forest Carbon (ForC) database

### 2021-01-19 manuscript/response_to_reviews.Rmd

---
\raggedright

**Title:** Response to reviews

Re: "Carbon cycling in mature and regrowth forests globally" by Anderson-Teixeira, Kristina; Herrmann, Valentine; Banbury Morgan , Rebecca ; Bond-Lamberty, Benjamin; Cook-Patton, Susan; Ferson , Abigail; Muller-Landau, Helene; Wang, Maria
Article reference: ERL-109898

## LETTER TO EDITOR:

The most substantive changes included the following:

- Changed the figure set in accordance with comments from R3. Specifically, we
(1) added a schematic figure, somewhat in the style of @odum_strategy_1969, to help with conceptual framing of the review
(2) added figures synthesizing changes in fluxes through time for each biome;
(3) removed maps from age trend diagrams (available in SI) from age trend diagrams, which makes the figures less busy/ easier to read; and
(4) moved C cycle diagrams for young forests to SI;

- Improved conceptual framework and "review" nature of the work by adding background information to the introduction, including the schematic figure mentioned above. We also shifted emphasis more towards the ecological questions (trends across biomes and with age), while retaining (with less emphasis) the analysis of database representativeness.

\newpage

## REFEREE REPORT(S) & RESPONSES:

@@

3. There is a general sloppiness to the manuscript that makes me think the authors did not proofread the manuscript carefully.

*This is true. Need to fix all points below. None difficult.*

a. Line 58: The authors say GPP is estimated to be >69 Gt C/year, and cite Badgley et al. (2019). This statement is factually correct, but is quite misleading. Badgley et al. "estimate global annual terrestrial photosynthesis to be 147 Pg C/year (95% credible interval 131-163 Pg C/year)". The value of 69 Gt C is less than one-half that reported by Badgley. What are the authors trying to say? Such a large discrepancy does not instill confidence in the other numbers reported in the manuscript.

**The 147 refers to *total* annual terrestrial photosynthesis, including non-forests. Table S4 breaks this down by biome. The >69 Gt C/yr figure was obtained by summing the forest biomes, not including savannas.**

### 2021-01-19 manuscript/ERL_global_C_review.Rmd
small updates

*Background.* Earth’s climate is closely linked to forests, which strongly influence atmospheric carbon dioxide (CO~2~) and climate by their impact on the global carbon (C) cycle. However, efforts to incorporate forests into climate models and CO~2~ accounting frameworks have been constrained by a lack of accessible, global-scale data on how C cycling varies across forest types and stand ages.

@@

*Review Results/ Synthesis.*  *ForC v3.0* yielded a comprehensive picture of C cycling in the world's major forest biomes. The rate of C cycling generally increased from boreal to tropical regions in both mature and regrowth forests, whereas C stocks showed less directional variation. The majority of flux variables, together with most live biomass pools, increased significantly with stand age. Importantly, there was generally good closure of C budgets, *i.e.,* internal consistency in the *ForC* data.

*Discussion.* As climate change accelerates, understanding and managing the carbon dynamics of forests is critical to forecasting, mitigation, and adaptation. This synthetic and internally consistent global overview of C stocks and fluxes across biomes and stand ages will help to advance these efforts.

@@

Forest C cycling varies enormously across biomes, which are artificial categorical distinctions convenient for categorizing the world's forests according to major differences in climate, vegetation, *etc.* 
Since *(Humboldt?)*, it has been recognized that climate plays a dominant role in shaping differences among forests.
Early quantitative syntheses revealed that C fluxes such as net primary productivity ($NPP$) decrease dramatically with latitude, or increase across gradients of mean annual temperature and, to a lesser extent, precipitation [@lieth_primary_1973].

@@

While current data and technology allow increasingly fine-scale resolution for understanding differences across forests, cateogorization into biomes remains useful for applications where data do not yet support robust analysis across finer-scale axes of variation.

>>>>

*Background.* Earth’s climate is closely linked to forests, which strongly influence atmospheric carbon dioxide (CO~2~) and climate by their impact on the global carbon (C) cycle. However, efforts to incorporate forests into climate models and CO~2~ accounting frameworks have been constrained by a lack of accessible, global-scale synthesis on how C cycling varies across forest types and stand ages.

@@

*Review Results/ Synthesis.*  *ForC v3.0* yielded a comprehensive picture of C cycling in the world's major forest biomes. The rate of C cycling generally increased from boreal to tropical regions in both mature and regrowth forests, whereas C stocks showed less directional variation. The majority of flux variables, together with most live biomass pools, increased significantly with stand age. There was generally good closure of C budgets for mature forests, whereas age trends and C budget closure in young forests remain less clearly resolved.

*Discussion.* As climate change accelerates, understanding and managing the carbon dynamics of forests is critical to forecasting, mitigation, and adaptation. This synthetic global overview of C stocks and fluxes across biomes and stand ages will help to advance these efforts.

@@

Forest C cycling varies enormously across biomes, which are artificial categorical distinctions convenient for categorizing the world's forests according to major differences in climate, vegetation, *etc.* 
Since the early 19th century, it has been recognized that climate plays a dominant role in shaping differences among forests on a global scale [@humboldt_essay_1807; @holdridge_determination_1947].
Early quantitative syntheses revealed that C fluxes such as net primary productivity ($NPP$) decrease dramatically with latitude, or increase across gradients of mean annual temperature and, to a lesser extent, precipitation [@lieth_primary_1973].

@@

While current data and technology allow increasingly fine-scale resolution for understanding differences across forests, categorization into biomes remains useful for applications where data do not yet support robust analysis across finer-scale axes of variation.
